---
title: "Sam Matema Analysis"
author: "Shylock"
date: "6/4/2020"
output:
  html_document:
    df_print: paged
word_document:
  reference_docx: word-styles-reference.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('~/R/smatema/read_data001.R', echo=FALSE)

```

# Demographics table

```{r table01, message=FALSE, echo=FALSE, results='asis'}
tab1 <- tableby(genderhousehold ~., data=dem)
summary(tab1)
```

## Summary of roster (skills, education, etc )

```{r table02, echo=FALSE, message=FALSE, results='asis'}

tab2 <- tableby(sec1q2 ~., data=roster)
summary(tab2)
```


##  Food security

This section discusses the food security situation over the past five years,... 
```{r table03, echo=FALSE, message=FALSE, results='asis'}
tab3 <- tableby(genderhousehold ~., data=fs)
summary(tab3)
```

## What are the main shocks

```{r table04, results='asis'}
tab4 <- tableby(genderhousehold ~., data=shocks)
summary(tab4)
```

## Adaptation to shocks 

```{r table05, results='asis'}
tab5 <- tableby(sec3b1 ~., data=adaptation)
summary(tab5)
```

## Section 4A: Shocks and local knowledge

```{r table06, results='asis'}
tab6 <- tableby(sec4a2 ~., data=iks)
summary(tab6)
```

When asked if these prediction systems are useful, the community members indicated the following: 

```{r table07, results='asis'}
tab7 <- tableby(genderhousehold ~., data=iks2)
summary(tab7)
```

## Section 5: Access to programmes and services by gender of household

```{r table16, message=FALSE, echo=FALSE, results='asis'}
tab16 <- tableby(genderhousehold ~ Programmes + Source, data=sam_data_007)
summary(tab16)
```

<<<<<<< HEAD
## Section 4C: Sacred animals, birds, and animals

```{r table08, results='asis'}
tab8 <- tableby(section4c_sec4c1a ~., data=abt)
summary(tab8)
```


## Section 6C: Crop production major crops grown and production levels 

```{r table09ab, results='asis'}
tab09 <- tableby(sec6c1 ~., data=crops)
summary(tab09)
```

## Section 6D: Crop production-dropped since 1980

```{r table10ab, results='asis'}
tab010 <- tableby(sec6d_sec6d1 ~., data=crops_1980)
summary(tab010)
```


## Section 6D: Crop production-adopted since 1980

```{r table011a}
tab011 <- tableby(sec6dd_sec6d3 ~., data=crops_1980a)
summary(tab011)
```

<<<<<<< HEAD
## Section 5: Sources of programmes and services

```{r table15, message=FALSE, echo=FALSE, results='asis'}
tab15 <- tableby(Source ~ Programmes, data=sam_data_007)
summary(tab15)
```

<<<<<<< HEAD
## Section 7B: Awareness

```{r table10, message=FALSE, echo=FALSE, results='asis'}
tab10 <- tableby(Awareness ~Rule, data=sam_data_014)
summary(tab10)
```

## Section 7B: Compliance

```{r table11, message=FALSE, echo=FALSE, results='asis'}
tab11 <- tableby(Compliance ~Rule, data=sam_data_014)
summary(tab11)
```

## Section 9: Source of livelihood by gender of household head

```{r table12, message=FALSE, echo=FALSE, results='asis'}
tab12 <- tableby(genderhousehold ~Livelihood_source, data=sam_data_016)
summary(tab12)
```

## Section 10: Forest resources by time of main consumption during the year

```{r table13, message=FALSE, echo=FALSE, results='asis'}
tab13 <- tableby(Time_of_year ~ Product, data=sam_data_017)
summary(tab13)
```

## Section 10: Forest resources by selling

```{r table14, message=FALSE, echo=FALSE, results='asis'}
tab14 <- tableby(Does_hh_sell ~ Product, data=sam_data_017)
summary(tab14)
```
=======
```{r table10a, results='asis'}
tab10 <- tableby(Enforcer ~., data=sam_data_014)
summary(tab10)
```
>>>>>>> ae1aa9e705fe62ea9514e0cba0c698a09cede8ae
>>>>>>> f43b29714a233655e5a647ca903abc5da22cd0f7
